---
title       : Eat and Play Team
subtitle    : China Company US Stock Analysis
author      : Yi Li, Zhang Qin, Zhaoqin Ye
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

--- &twocol
## Eat and Play Team: China Company US Stock Analysis

- question answered:
  - What are some patterns in the decomposition of China companies' US Stock
  - How do these stocks perform compared to US stocks from 2005 to present
  - how do these stocks perform compared to Chinese domestic stocks from 2005 to present

## Chinese company US stock decomposition
- dataset: NASDAQ, NYSE, AMEX exchanges stock listing (variables: symbol, sector, IPOyear, exchange)
*** =left
```{r echo=FALSE,message=FALSE,out.width='400px',out.height='250px'}
library(DataComputing)
dataPath <- "~/Desktop/proj/data/"
ChinainUS <- read.csv(file=paste(dataPath, "ChinaStockInUS.csv", sep="")) %>%
  filter(Sector!="n/a")
SectorCount <- ChinainUS %>%
  group_by(Sector) %>%
  summarise(Count=n()) %>%
  arrange(desc(Count)) %>%
  mutate(Percentage=paste(round(100*Count/nrow(ChinainUS), 2), "%", sep=""))
SectorCount %>%
  transform(Sector = reorder(Sector, Count)) %>%
  ggplot(aes(x=Sector, y=Count, fill=Sector)) +
    geom_bar(stat="identity") + 
    coord_flip() +
    ylab("Number of Companies") + 
    theme(legend.position="none")
```
Technology dominates all other sectors, so we choose to use this sector's stocks for further comparison with different markets

*** =right
```{r echo=FALSE,message=FALSE,out.width='400px',out.height='250px'}
NYSE <- read.csv(file=paste(dataPath, "NYSE.csv", sep=""))
NASDAQ <- read.csv(file=paste(dataPath, "NASDAQ.csv", sep=""))
AMEX <- read.csv(file=paste(dataPath, "AMEX.csv", sep=""))
for (i in 1:nrow(ChinainUS)){
  if (ChinainUS$Symbol[i] %in% NYSE$Symbol){
    ChinainUS$Exchange[i]="NYSE"
  }else if(ChinainUS$Symbol[i] %in% NASDAQ$Symbol){
    ChinainUS$Exchange[i]="NASDAQ"
  }else if(ChinainUS$Symbol[i] %in% AMEX$Symbol){
    ChinainUS$Exchange[i]="AMEX"
  }else{
    ChinainUS$Exchange[i]="Other"
  }
}
ChinainUS %>%
  filter(IPOyear!="n/a")%>%
  ggplot(aes(IPOyear))+geom_bar(aes(fill=Exchange),position="stack")+
    theme(legend.position="top",axis.text.x = element_text(angle =30,hjust = 1))
```

NYSE has more in past, but NASDAQ increases greatly and exceeds NYSE in recent years

--- &twocol

## Performance against US stocks

- method learned in class: 
  - use XML library to scrape data table in HTML page
  - convert all history data to same tiny data format
  - process and mutate date variables in R
- dataset: 
  - Top technology ETFs listing (variables: symbol)
  - Yahoo Finance stock history price (variables: date, Close price)

*** =left
```{r echo=FALSE,message=FALSE,out.width='500px',out.height='300px'}
getStockTimeSeries <- function(filePath, title) {
  stock <- read.csv(filePath) %>%
    mutate(date=as.Date(Date), price=Close) %>%
    filter(year(date) >= 2005) %>%
    select(date, price)
  return(mutate(stock, title=rep(title, nrow(stock))))
}

getStocksAverageTimeSeries <- function(folderPath, title) {
  files <- list.files(folderPath)
  stock <- read.csv(paste(folderPath, files[1], sep=""))
  for (i in 2:length(files)) {
    stock <- rbind(stock, read.csv(paste(folderPath, files[i], sep="")))
  }
  stock <- stock %>%
    mutate(date=as.Date(Date)) %>%
    group_by(date) %>%
    summarise(price=mean(Close)) %>%
    filter(year(date) >= 2005) %>%
    select(date, price)
  return(mutate(stock, title=rep(title, nrow(stock))))
}

plotSingleTimeSeries <- function(timeSeries) {
  ggplot(timeSeries, aes(x=date, y=price)) + 
    geom_line(color="blue")
}

plotMultipleTimeSeries <- function(timeSeriesList) {
  tbl <- timeSeriesList[[1]]
  for (i in 2:length(timeSeriesList)) {
    tbl <- rbind(tbl, timeSeriesList[[i]])
  }
  ggplot(tbl, aes(x=date, y=price, color=title)) + 
    geom_line()
}

ChinaTechInUS <- getStocksAverageTimeSeries(paste(dataPath, "ChinaTechInUS/",sep=""),"ChinaTechInUS")
timeSeriesList <- list(ChinaTechInUS)
USETFPath <- paste(dataPath, "USTechETF/", sep="")
total <- 1
for (etf in list.files(USETFPath)) {
  total <- total + 1
  newTimeSeries <- getStockTimeSeries(paste(USETFPath, etf, sep=""), gsub("(history_|.csv)","",etf))
  timeSeriesList[[total]] <- newTimeSeries
}
plotMultipleTimeSeries(timeSeriesList)
```
China company's stocks do not perform as well as US stocks in tech sector

*** =right
```{r echo=FALSE,message=FALSE,out.width='500px',out.height='300px'}
timeSeriesList <- list()
USETFPath <- paste(dataPath, "ChinaTechUSETF/", sep="")
total <- 1
for (etf in list.files(USETFPath)) {
  total <- total + 1
  newTimeSeries <- getStockTimeSeries(paste(USETFPath, etf, sep=""), gsub("(history_|.csv)","",etf))
  timeSeriesList[[total]] <- newTimeSeries
}
USETFPath <- paste(dataPath, "USTechETF/", sep="")
for (etf in list.files(USETFPath)) {
  total <- total + 1
  newTimeSeries <- getStockTimeSeries(paste(USETFPath, etf, sep=""), gsub("(history_|.csv)","",etf)) %>%
    filter(year(date) >= 2010)
  timeSeriesList[[total]] <- newTimeSeries
}
plotMultipleTimeSeries(timeSeriesList)
```
Three ETFs of China stocks also indicates the low performance against foreign stocks in same category

--- &twocol

## Performance against Chinese domestic stocks
- method not in class: 
  - data scraping for non-html tables, using Scraper plugin in Chrome
  - deal with non-ASCII encoded data table information
  - clean HTML page for link tag information as data input using XPathApply
- dataset:
  - Chinese stock listing by sector (variables: symbol, exchange, sector)
  - Yahoo Finance stock history price (variables: date, Close price)

*** =left
```{r echo=FALSE,message=FALSE,out.width='500px',out.height='300px'}
ChinaSoftwareRMB <- getStocksAverageTimeSeries(paste(dataPath, "ChinaTech/Software/",sep=""),"ChinaSoftware")
ChinaHardwareRMB <- getStocksAverageTimeSeries(paste(dataPath, "ChinaTech/Hardware/",sep=""),"ChinaHardware")
ChinaTechRMB <- rbind(ChinaSoftwareRMB, ChinaHardwareRMB) %>%
  group_by(date) %>%
  summarise(price=mean(price))
ChinaTechRMB <- mutate(ChinaTechRMB, title=rep("ChinaTech", nrow(ChinaTechRMB)))
timeSeriesList <- list(ChinaTechInUS, ChinaTechRMB, ChinaSoftwareRMB, ChinaHardwareRMB)
plotMultipleTimeSeries(timeSeriesList)
```
Follow very similar patterns, especially from 2009-2014, but starting from 2014 domestic tech stocks tend to outperform foreign stocks due to China's tech boom

*** =right
```{r echo=FALSE,message=FALSE,out.width='500px',out.height='300px'}
timeSeriesList <- list(filter(ChinaTechRMB, year(date) >= 2010))
USETFPath <- paste(dataPath, "ChinaTechUSETF/", sep="")
total <- 1
for (etf in list.files(USETFPath)) {
  total <- total + 1
  newTimeSeries <- getStockTimeSeries(paste(USETFPath, etf, sep=""), gsub("(history_|.csv)","",etf))
  timeSeriesList[[total]] <- newTimeSeries
}
plotMultipleTimeSeries(timeSeriesList)
```
ETFs follow similar pattern to domestic average, further indicating domestic stock influence to foreign China stock price
